
\section*{CIVIS Consortium}
CIVIS (Grant Agreement contract No. 608774) is a Collaborative Project within the 7th Framework Programme, theme FP7-SMARTCITIES-2013, ICT-2013.6.4. As defined in the Consortium Agreement [2], members of the Consortium are:

\vspace{.2cm}

\begin{longtable}{|c|p{14.5cm}|}
\hline
\textbf{No.} & \textbf{Beneficiaries} \\ \hline
1 &	UNIVERSITA DEGLI STUDI DI TRENTO, established in VIA CALEPINA 14, 38122 TRENTO - ITALY, represented by Mr Paolo COLLINI, Rector, or his authorised representative, the beneficiary acting as coordinator of the consortium (the "coordinator"). \\ \hline
2 &	AALTO-KORKEAKOULUSAATIO established in OTAKAARI 1, 00076 AALTO -
FINLAND, represented by Mr Ilkka NIEMEL\"{A}, Deputy President and/or Mr Tuija PULKKINEN,
Vice President, or their authorised representative. \\ \hline
3 &	FONDAZIONE CENTRO STUDI ENEL established in VIALE REGINA MARGHERITA 137, 00198 ROMA - ITALY, represented by Mr Francesco STARACE, President, or his authorised representative. \\ \hline
4 &	IMPERIAL COLLEGE OF SCIENCE, TECHNOLOGY AND MEDICINE established
in Exhibition Road, South Kensington Campus, SW7 2AZ LONDON - UNITED KINGDOM, represented by Ms Carole MEADS, Senior Negotiator, European Policy and/or Mr James LLOYD, Contracts Administrator (Europe), or their authorised representative. \\ \hline
5 &	INSTITUTO SUPERIOR TECNICO established in Avenida Rovisco Pais 1, 1049-001 LISBOA - PORTUGAL, represented by Mr Arlindo OLIVEIRA, President, or his authorised representative. \\ \hline
6 &	Karlsruher Institut fuer Technologie established in Kaiserstrasse 12, 76131 Karlsruhe - GERMANY, represented by Mr Bernhard DASSELAAR, Head of Cost and Fund Management and/or Mr Wolf FICHTNER, Head of IIP, or their authorised representative. \\ \hline
7 &	KUNGLIGA TEKNISKA HOEGSKOLAN established in BRINELLVAGEN 8, 100 44
STOCKHOLM - SWEDEN, represented by Mr Peter GUDMUNDSON, President and/or Mr Kenneth BILLQVIST, Head of Research Office, or their authorised representative. \\ \hline
8 &	SANTER REPLY SPA established in VIA ROBERT KOCH 1/4, 20152 MILANO - ITALY, represented by Mr Luigi CICCHESE, Partner, or his authorised representative. \\ \hline
9 &	NEDERLANDSE ORGANISATIE VOOR TOEGEPAST NATUURWETENSCHAPPELIJK ONDERZOEK - TNO established in Schoemakerstraat 97, 2600 JA DELFT - THE NETHERLANDS, represented by Drs. Ren\'{e} HOOIVELD, Director of Sustainable
Energy, or his authorised representative. \\ \hline
10 &	TECHNISCHE UNIVERSITEIT DELFT established in Stevinweg 1, 2628 CN DELFT - THE NETHERLANDS, represented by Mr Jeroen VAN DEN HOVEN, Dean and/or Mr Hans DE BRUIJN, Vice-Dean, or their authorised representative. \\ \hline
11 &	CREATE-NET (CENTER FOR RESEARCH AND TELECOMMUNICATION
EXPERIMENTATION FOR NETWORKED COMMUNITIES) established in VIA ALLA CASCATA 56/D, 38123 TRENTO - ITALY, represented by Mr Imrich CHLAMTAC, President, or his authorised representative. \\ \hline
12 &	FONDAZIONE BRUNO KESSLER established in VIA SANTA CROCE 77, 38122
TRENTO - ITALY, represented by Mr Andrea SIMONI, General Secretary and/or his authorised representative. \\ \hline
\end{longtable}

\clearpage


{\hypersetup{linkcolor=black}
\tableofcontents}
